---
title: "cyclingtools"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{cyclingtools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  dpi = 300
)
```

```{block, type = 'rmdinfo'}
Please, note that currently `cyclingtools` only provide **critical power** analyses. However, more functionality is planned, such as training impulse analyses (iTRIMP, bTRIMP, eTRIMP, luTRIMP).

If you have a suggestion, feel free to open an issue.
```

## Critical Power analysis

For performing **critical power** analysis, the general `critical_power()` function was created. There are basically two main options in there: you can choose which model to fit (i.e., CP 3-hyp, CP 2-hyp, CP linear, and CP 1/time), and you can also choose whether to produce an analysis with all the combinations of the time-to-exhaustion trials provided.

Let's look at the main functionality:

```{r echo=TRUE}
library(cyclingtools)

simple_results <- critical_power(
  .data = demo_data, 
  power_output_column = "PO", 
  time_to_exhaustion_column = "TTE", 
  method = c("3-hyp", "2-hyp", "linear", "1/time"), 
  plot = TRUE, 
  all_combinations = FALSE
)

simple_results
```

In the above example, we chose to fit critical power on all the available methods, but you can also just choose one or two:

```{r}
critical_power(
  .data = demo_data, 
  power_output_column = "PO", 
  time_to_exhaustion_column = "TTE", 
  method = c("3-hyp", "2-hyp"), 
  plot = TRUE, 
  all_combinations = FALSE
)
```

The nice thing about the retrieved results is that the **model** is saved as well. So you can further explore it if you would like to. For example, using the base R function `summary()`:

```{r}
simple_results %>% 
  dplyr::slice(1) %>% 
  dplyr::pull(model) %>% 
  .[[1]] %>% 
  summary()
```

Or the `broom::tidy()` function:

```{r}
simple_results %>% 
  dplyr::slice(1) %>% 
  dplyr::pull(model) %>% 
  .[[1]] %>% 
  broom::tidy()
```

The above can also be more quickly achieved with the following:

```{r}
simple_results %>% 
  dplyr::select(method, model) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(tidy_model = broom::tidy(model) %>% list()) %>% 
  tidyr::unnest(cols = tidy_model)
```

## Multiple combinations

The `all_combinations` argument let you decide whether to perform multiple fits from all the possible combinations of trials provided:

```{r}
combinations_results <- critical_power(
  .data = demo_data, 
  power_output_column = "PO", 
  time_to_exhaustion_column = "TTE", 
  method = c("3-hyp", "2-hyp", "linear", "1/time"), 
  plot = TRUE, 
  all_combinations = TRUE
)

combinations_results
```

You can also check the plots of each estimation in case you set `plot = TRUE`:

```{r}
combinations_results %>% 
  dplyr::slice(10) %>% 
  dplyr::pull(plot)
```

## Individual functions

Please, note that `critical_power()` is a general function that makes your life easier. However, you can also call the individual functions of each method:

* `method_3_hyp()` = 3-parameter hyperbolic model
* `method_2_hyp()` = 2-parameter hyperbolic model
* `method_linear()` = linear model
* `method_1_time()` = 1/time linear model

Example:

```{r}
method_3_hyp(
  .data = demo_data, 
  power_output_column = "PO", 
  time_to_exhaustion_column = "TTE", 
  plot = TRUE
)
```

## Shiny app

All of these functions can be performed in [Critical Power Dashboard](https://www.shiny.fmattioni.me/CPapp/)
